---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# numerizer

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

The goal of numerizer is to Parse Numbers in Natural Language from Strings

# Installation

You can install the released version of numerizer from [CRAN](https://CRAN.R-project.org) with:

### Stable Version

``` r
#install.packages("numerizer")
```

### Development Version

```
#using remotes
remotes::install_github("amrrs/numerizer")

#using devtools
devtools::install_github("amrrs/numerizer")
```

# Requirements

This package requires the original Python package [`numerizer`](https://github.com/jaidevd/numerizer). In case if you don't have, please make sure to install it in your default Python environment.

```python
pip install numerizer
```




# Loading the package

```{r package}
library(numerizer)
```

# Examples


```{r}
numerize('twenty one thousand four hundred and seventy three')

numerize('one million two hundred and fifty thousand and seven')
```

